%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {Payfit} % Organization
    {Paris, France} % Location
    {Mar. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Day to day}: supporting developpers with their use of the internal infrastructure (\emph{e.g.} terraform, kubernetes or datadog); general gardening of our infra-as-code codebase (\emph{e.g.} terraform modules or gitops repositories).}
        \item {\textbf{Observabiliy evangelism} by writting internal guidelines and pushing industry best-practices.}
        \item {\textbf{Terraform evanglism} by co-authoring the internal guidelines and pushing industry best-practices. As well as driving initiation workshops.}
        \item {\textbf{Datadog optimization}: setup automation with Terraform (AWS integration, forwarder deployment, RBAC management and log exclusion rules); deploying finops tools to help with cost control and decision making for contract renewals; reduced our annual billing by 30\% in two year by reworking log indexation, custom metrics consumption and agent deployments and by 50\% our data ingestion costs by deploying Vector as an aggregator }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {Aircall} % Organization
    {Paris, France} % Location
    {Nov. 2021 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Day to day}: supporting developpers with their use of the internal infrastructure (\emph{e.g.} Terraform, AWS or Datadog); general gardening of our infra-as-code codebase (\emph{e.g.} terraform modules or AWS automation).}
        \item {\textbf{Observabiliy evangelism} by pushing industry best-practices.}
        \item {\textbf{Datadog optimization}: setup automation with Terraform; deploying finops tools to help with cost control and decision making for contract renewals.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {ManoMano} % Organization
    {Paris, France} % Location
    {Sep. 2019 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Operational support} ranging from issue or performance debugging to application architecture to AWS services deployments (EC2, ECS, RDS, Elasticache, ...).}
        \item {\textbf{Terraform and Terragrunt evangelism} by writing internal guidelines and refactoring our infra-as-code monorepo to make the most use of Terragrunt.}
        \item {\textbf{Tooling development} ranging from a RabbitMQ log audit daemon to python scripts and shell snippets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer/Backend developer} % Job title
    {Gabsee} % Organization
    {Paris, France} % Location
    {Mar. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Infrastructure automation} with Terraform and the development of several in-house modules.}
        \item {\textbf{Immutable deployments} with with Packer.}
        \item {\textbf{Developed a Restful API} around Consul's and Nomad's API to implement an intelligent orchestration layer for our game servers.}
        \item {\textbf{Backend development} with a Restful API written in Go and Buffalo.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Ogury} % Organization
    {Paris, France} % Location
    {Feb. 2018 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Infrastructure automation} with Cloudformation and Chef.}
        \item {\textbf{Scripts development} in Python or Bash to automize procedures (building temporary infrastructure, creating/restoring backups, ...)}
        \item {\textbf{Tooling development} in Go to backup and restore AWS Cognito identity pools.}
        \item {\textbf{Operational support} to the developpers, like helping them with designing their infrastructures to better suits their need.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud \& Automation Consultant} % Job title
    {D2SI} % Organization
    {Paris, France} % Location
    {Oct. 2016 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Operational support} ranging from issue or performance debugging to building Docker images, CI workflows, local development stacks or AWS infrastructures.}
        \item {\textbf{Infrastructure automation} with Terraform, Packer, Bash, Ansible and Python.}
        \item {\textbf{Managed and mentored} an intern for 6 months. Working on Docker related themes such as Data persistency and orchestration solutions benchmarking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Cloud Engineer (Trainee)} % Job title
  %   {Linagora} % Organization
  %   {Puteaux, France} % Location
  %   {Oct. 2015 - Exp. Oct. 2016} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Built multiple docker-compose's and images for different in-house projects}
  %       \item {Deployed a Ceph cluster (made of 3 nodes) and integrated it to OpenStack's Cinder storage service}
  %       \item {Automated a Kubernetes infrastructure on OVH's public cloud platform, based on Terraform and CoreOS}
  %       \item {Installed a DevStack instance as a quick'n'dirty testing platform}
  %       \item {Provided Docker 101 formations and support to the other teams}
  %       \item {Created a private Docker registry using Port.us}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  % \cventry
  %   {Developer Engineer (Trainee)} % Job title
  %   {Thales Services} % Organization
  %   {Velizy, France} % Location
  %   {Sept. 2014 - Exp. Sept. 2015} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %         \item {Research and development on the RBAC pattern and introducing it to the team}
  %         \item {Built a Restful API based on Symfony 2 and a web client using AngularJS 1.4}
  %         \item {Continuous integration and deployment with Jenkins, SonarQube and Capistrano}
  %         \item {Researched on the DevOps methodologies and started promoting it to the team}
  %         \item {Deployed a reverse-proxy for our software factory using HAProxy}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
